---
title: "AE 11: Midterm Pokémon Practice"
---

In this AE, you'll work through some variety of tasks to prepare for the midterm while learning about the Pokémon universe!

```{r}
#| message: false
library(tidyverse)
```

```{r}
pokemon <- read_csv("data/pokemon.csv")
pokemon_go <- read_csv("data/pokemon_go.csv")
```

## Question 1

Take a look at the data with an appropriate function.
Report the number of rows and colmns in each one.
Note that each row refers to a single Pokémon.

```{r}
#| label: firstlook

```

## Question 2

Using the first data set, create a density plot of all water type's `hp`.
Note that a Pokémon is considered a water type if either its `type_1` or `type_2` is water.
Describe the distribution with appropriate summary statistics.

```{r}
#| label: water

```

## Question 3

Create a table that displays the number of legendary Pokémon (`is_legendary`) from each (`type_1`) in descending order.

```{r}
#| label: legend_table

```

## Question 4

Using the table above, make a barplot with n on the x-axis, but make sure that the order of the types in the first column is preserved

```{r}
#| label: namesinorder

```

## Question 5

Pokémon and Pokémon Go are actually very different games.
You want to investigate if there is any relationship between the `attack` variable in Pokémon and the `base_attack` in Pokémon Go.
The variables lie in different datasets however.

In a single pipeline, create a scatterplot that visualizes the relationship above.
Only include Pokémon who are present in both games.
Describe the distribution

```{r}
#| label: pokejoin

```
