---
title: "AE 11: Midterm Pokémon Practice"
---

In this AE, you'll work through some variety of tasks to prepare for the midterm while learning about the Pokémon universe! 

```{r}
#| message: false
library(tidyverse)
```

```{r}
pokemon <- read_csv("data/pokemon.csv")
pokemon_go <- read_csv("data/pokemon_go.csv")
```

## Question 1

Take a look at the data with an appropriate function. Report the number of rows and colmns in each one. Note that each row refers to a single Pokémon. 

```{r}
#| label: firstlook
glimpse(pokemon)
glimpse(pokemon_go)
```

## Question 2 

Using the first data set, create a density plot of all water type's `hp`. Note that a Pokémon is considered a water type if either its `type_1` or `type_2` is water. Describe the distribution with appropriate summary statistics. 

```{r}
#| label: water
water_poke <- pokemon |> 
  filter(type_1 == "Water" | type_2 == "Water")

ggplot(water_poke, aes(x = hp)) +
  geom_density() +
  labs(x = "HP",
       title = "HP of Water Type Pokémon")

water_poke |> 
  summarise(mean = mean(hp),
            median = median(hp),
            sd = sd(hp),
            iqr = IQR(hp))
```
The distribution of water type hp is unimodal and right skewed, with potential outliers on the right tail past 180, with a mean of 69.7 and median or 70 and a standard deviation of 26.26 and iqr of 35.

## Question 3

Create a table that displays the number of legendary Pokémon (`is_legendary`) from each (`type_1`) in descending order. 

```{r}
#| label: legend_table
leg_tab <- pokemon |> 
  filter(is_legendary == TRUE) |> 
  group_by(type_1) |> 
  summarise(n = n()) |> 
  arrange(desc(n))
```

## Question 4

Using the table above, make a barplot with n on the x-axis, but make sure that the order of the types in the first column is preserved

```{r}
#| label: namesinorder
ggplot(leg_tab, aes(x = n, y = fct_reorder(type_1, n))) +
  geom_col() +
  labs(y = "Type",
       title = "Number of Legendary Pokémon by Type")
```

## Question 5

Pokémon and Pokémon Go are actually very different games. You want to investigate if there is any relationship between the `attack` variable in Pokémon and the `base_attack` in Pokémon Go. The variables lie in different datasets however. 

In a single pipeline, create a scatterplot that visualizes the relationship above. Only include Pokémon who are present in both games. Describe the distribution

```{r}
#| label: pokejoin
pokemon |> 
  inner_join(
    pokemon_go,
    by = join_by(name == pokemon_name)
  ) |> 
  ggplot(aes(x = attack, y = base_attack)) +
  geom_point() +
  labs(x = "Attack",
       y = "Base Attack",
       title = "Base Attack by Attack of Pokémon in Both Games")
```
There is a strong, positive, roughly linear relationship between the base attack (present in Pokémon Go) and attack (present in Pokémon) of Pokémon found in both games. 





